Summer 2025 ToDo

### 2025-04-23 Relations/Paper/Summer_2025_TODO.tex
Minor update to wellfounded

  \item Other ToDo 
  \begin{todolist}
    \item Make Latex version of WF implications .
    \item Verify which implications have and have not been formalized from the image.
  \end{todolist}
\end{itemize}
\end{document}

>>>>

  \item Other ToDo 
  \begin{todolist}
    \item [\done] Make Latex version of WF implications (initial draft).
    \item Verify which implications have and have not been formalized from the image.
    \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$. 
    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
    \item (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition. 
    \item Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper. I need to go through it and either understand it or come with questions to Friday's meeting.
  \end{todolist}
\end{itemize}
\end{document}
